\chapter{Face and Body Pose Tracking} \label{applications}

Chapter \ref{system} presented an integrated vision system for \RD{}, and Chapter \ref{depthcolor} showed 
that it is possible to build new camera representations on top of it. Along with capturing and handling images, 
a vision system should be able to retrieve information from them. This chapter integrates two algorithms in the 
field of object detection and tracking that let the system gather information about humans in the 
camera's surroundings. 

Section \ref{facetracker} presents a face tracking algorithm that operates on the depth-color images introduced 
in Chapter \ref{depthcolor}. This algorithm uses the depth information to segment the person of interest from 
the background and consequently reduce the number of false positives detected by a traditional face detector.
The algorithm is shown to be robust to different face positions and orientations. 

Section \ref{bodyposetracker} introduces a representation for the Microsoft's Kinect camera and integrates an
open source framework that uses the Kinect's images to detect and track a person's body pose. The algorithm 
implemented in this framework operates on the depth images captured by the Kinect and outputs a body 
skeleton indicating the position and orientation of various joints in the human body. 

In this chapter, the Kinect becomes the second depth-color camera that forms part of the integrated vision 
system. In conjunction with the two tracking algorithms, this serves to point out the new importance of these 
sensors in the field of computer vision. 


\section{Face Tracker} \label{facetracker}
\input{applications/facetracker}

\section{Body Pose Tracker} \label{bodyposetracker}
\input{applications/bodyposetracker}